Supporting Information for "Geometric models overestimate lake depth due to imperfect slope measurement"

### 2020-12-03 manuscript/si_template_2019.tex
add calc techniques to figs6 caption
add takeaway to figs6 caption

\begin{figure}
      \begin{center}
        \includegraphics[width=\textwidth,keepaspectratio]{../figures/01_slope_compare-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slope using different calculation techniques. See Table S2 for explanation of each.}\label{figS6}
    \end{figure}
\clearpage

>>>>

\begin{figure}
      \begin{center}
        \includegraphics[width=\textwidth,keepaspectratio]{../figures/01_slope_compare-1}
      \end{center}
      \caption{Comparison between in-lake and nearshore slope using different calculation techniques. The techniques used in the main text analyses are bolded and the combination of these techniques (top-left corner) produces the strongest relationship between the two metrics. \texttt{slope\_mean} is the mean slope of all inlake or nearshore buffer points. \texttt{slope\_pnts} is the average \texttt{slope\_pnt} of all points at maximum depth. \texttt{slope\_online\_mean} is the mean pixel-to-pixel slope of each pixel lying on a straight line either from the single deepest point to the lake shoreline (in the case of inlake slope) or from the lake shoreline point extending to the buffer exterior (in the case of nearshore slope). \texttt{slopes\_online\_mean} is the same as \texttt{slope\_online\_mean} except for all inlake points at maximum depth. \texttt{dists\_deepest} is the same as \texttt{dist\_deepest} except distance is calculated for all points at maximum depth.}\label{figS6}
    \end{figure}
\clearpage
